\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 TPDP2018/poster/main.tex
fixing typos...

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Design a differentially private Bayesian inference mechanism.
\item Improve accuracy by calibrating noise  to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
\end{enumerate}
\end{block}

@@

\begin{block}{Bayesian inference ($\bysinfer$), the Beta-Binomial model example:}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item  Prior on {\small $\theta: \mathbb{P}_{\theta}= \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data $\dataobs= (x_1,\dots, x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.}

@@

\begin{block}{Differentially private Bayesian inference and motivations}
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
\item  Baseline approach: 
  \begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
  \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
  \end{itemize}
  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}. 
\item Another approach:
  \begin{itemize}
    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
    \end{itemize}
  \item A better approach:
    \begin{itemize}
      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
    \end{itemize}
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probability:
\[
\mathbb{P}_{r \thicksim \hexpmech} =
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]
where:
\begin{itemize}
 \small{ \item  $\betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$. With prior distribution $\bprior=\betad(\alpha, \beta)$.}
  \item \small{$-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function.}

@@

  \begin{block}{Preliminary experimental results}
    Experiments are about three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.

  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

@@

\begin{itemize}
  \item[-]  $\hexpmech$ outperforms the baseline approach but not the improved one.
  \item[-] By increasing the prior, $\hexpmech$ can outperform both the baseline approach and the improved one.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

@@

  %   \item Other application of our scheme are going to be explored.
  % \end{enumerate}
\end{itemize}
%\vspace{8mm}
%\vspace{8mm}
%where we require $t$ and $u$ to have distinct sets of free variables.
\end{block}

>>>>

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{itemize}
\item Design a differentially private Bayesian inference mechanism.
\item Improve accuracy by calibrating noise  to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
\end{itemize}
\end{block}

@@

\begin{block}{An example of Bayesian inference: the Beta-Binomial model}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item  Prior on {\small $\theta: \mathbb{P}_{\theta}= \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data $\dataobs= (x_1,\dots, x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.}

@@

\begin{block}{Differentially private Bayesian inference}
\begin{columns} % Subdivide the first main column
  \begin{column}{.69\textwidth}
    \vspace{-3cm}
\begin{itemize}
\item  Baseline approach: 
  \begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
  \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
  \end{itemize}
  \end{itemize}
  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}
    \vspace{-1cm}
\begin{itemize}
\item Another approach:
  \begin{itemize}
    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
    \end{itemize}
  \item A better approach:
    \begin{itemize}
      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
    \end{itemize}
\end{itemize}

@@

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probability:
\[
\mathbb{P}_{r \thicksim \hexpmech} =
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]
\begin{itemize}
 \small{ \item  $\betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$. With prior distribution $\bprior=\betad(\alpha, \beta)$.}
  \item \small{$-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function.}

@@

  \begin{block}{Preliminary experimental results}
    Experiments are about three mechanisms and plotted as follows:
\begin{itemize}
  \item {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.

  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

@@

\begin{itemize}
  \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
  \item By increasing the prior parameters, $\hexpmech$ can outperform both the baseline approach and the improved one.
  % \begin{itemize}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

@@

  %   \item Other application of our scheme are going to be explored.
  % \end{itemize}
\end{itemize}
%\vspace{8mm}
%\vspace{8mm}
%where we require $t$ and $u$ to have distinct sets of free variables.
\end{block}
